Community context determines competition vs. facilitation trade-offs in pollination systems

### 2019-06-07 paper/manuscript.Rmd
Minimal formatting for PLOS initial submission

**Running title:** 
Competition for pollination vs. facilitation

**Keywords:** `r keywords`

**Type of article:** Letter.

@@

**Number of references:** `r n_references`

@@

**Author contributions:** EFC wrote the manuscript and performed all analyses with input from all authors; HJM collected the data; all authors contributed to the study design.

>>>>

**Short title:** Competition for pollination vs. facilitation

<!-- **Keywords:** `r keywords` -->

**Type of article:** Primary research article

@@

<!-- **Number of references:** `r n_references` -->

@@

<!-- **Author contributions:** EFC wrote the manuscript and performed all analyses with input from all authors; HJM collected the data; all authors contributed to the study design.  -->

**Competing interests:** The authors have declared that no competing interests exist.
